A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-19 paper/draft.tex
include partisanship by occupation

It is important to note that the affiliation of party members has been increasing over time. Figure \ref{fig:number_partisanship} illustrates this pattern. The growth in the number of partisan affiliates has been rather rapid over time. While in the year 1997 there were around 200 thousand active party members, by the year 2018 this has increased to 10 million. While the causes of this rapid increase are not clear, it is most likely due to both increased registration and better quality data on partisan affiliation as the collection of information by the national electoral authority.

\begin{figure}[H]
    \centering
    \includegraphics[width = 10cm, height = 8cm]{figures/partisanship/plot_partisan_by_year.pdf}
    \caption{\textbf{Number of active party members by year}. There has been a rapid growth in the number of party members in the period between 1997 and 2020.}
    \label{fig:number_partisan}
\end{figure}

@@

Disaggregating the data further into regions, we find significant heterogeneities with respect to regional trends (Figure \ref{fig:number_partisan_region}).The region that concentrates the most rapid growth and the largest amount of party members is the Southeast, a densely populated and most economically developed region in Brazil. It is closely followed by the Northeast, a region that although relatively poor, has a been characterized by deep partisan roots that underlie patronage exchanges \citep{ansell2010auctioning}. The South, an affluent but predominantly rural region has similar levels of partisanship to the Northeast. In contrast, party membership in the Northern and Midwestern regions are low.

\begin{figure}[H]
    \centering
    \includegraphics[width = 10cm, height = 8cm]{figures/partisanship/plot_partisan_by_year.pdf}
    \caption{\textbf{Number of active party members by year}. There has been a rapid growth in the number of party members in the period between 1997 and 2020.}
    \label{fig:number_partisan_region}
\end{figure}

Regarding partisan duration spells, a few patterns emerge as in the. The spikes every four years mirror the jumps in partisanship in Figure \ref{fig:number_partisan} are mirrored

@@

\begin{figure}[H]
    \centering
    \includegraphics[width = 9cm, height = 9cm]{figures/maps/pooled.png}
    \caption{\textbf{Proportion of party-affiliated members by municipality (2015)}. Darker colors indicate a larger degree of partisan affiliation. Sample includes all bureaucrats, from high-level managers to service staff.}
    \label{fig:map_pooled}
\end{figure}

>>>>

It is important to note that the affiliation of party members has been increasing over time. Figure \ref{fig:number_partisan} illustrates this pattern. The growth in the number of partisan affiliates has been rather rapid over time. While in the year 1997 there were around 200 thousand active party members, by the year 2018 this has increased to 10 million. While the causes of this rapid increase are not clear, it is most likely due to both increased registration and better quality data on partisan affiliation as the collection of information by the national electoral authority.

\begin{figure}[H]
    \centering
    \includegraphics[width = 7cm, height = 7cm]{figures/partisanship/plot_partisan_by_year.pdf}
    \includegraphics[width = 7cm, height = 7cm]{figures/partisanship/plot_partisan_by_region.pdf}
    \caption{\textbf{Number of active party members by year}. Pooled (left) and disaggregated by region (right). There has been a rapid growth in the number of party members in the period between 1997 and 2020.}
    \label{fig:number_partisan}
\end{figure}

@@

Disaggregating the data further into regions, we find significant heterogeneities with respect to regional trends.The region that concentrates the most rapid growth and the largest amount of party members is the Southeast, a densely populated and most economically developed region in Brazil. It is closely followed by the Northeast, a region that although relatively poor, has a been characterized by deep partisan roots that underlie patronage exchanges \citep{ansell2010auctioning}. The South, an affluent but predominantly rural region has similar levels of partisanship to the Northeast. In contrast, party membership in the Northern and Midwestern regions are low.

Finally, we present data on party membership spells in Figure \ref{fig:party_spell}. A few patterns emerge. First, the distribution of spells is rather uniform, with spikes every four years that mirror the jumps in partisanship in Figure \ref{fig:number_partisan}.

\begin{figure}
    \centering
    \includegraphics[width = 10cm, height = 8cm]{figures/partisanship/plot_partisan_spell.pdf}
    \caption{\textbf{Party memebership spells}. Data includes all party memberships that start in 1985 - the Brazilian democratic transition - and 2019.}
    \label{fig:party_spell}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width = 8cm, height = 8cm]{figures/maps/pooled.png}
    \caption{\textbf{Proportion of party-affiliated members by municipality (2015)}. Darker colors indicate a larger degree of partisan affiliation. Sample includes all bureaucrats, from high-level managers to service staff.}
    \label{fig:map_pooled}
\end{figure}

Alongside these spatial differences, there are

\begin{figure}[H]
    \centering
    \includegraphics[width = 8cm, height = 8cm]{figures/partisanship/plot_partisanship_by_cbo_group.pdf}
    \caption{\textbf{Proportion of party-affiliated members by occupation}. Darker colors indicate a larger degree of partisan affiliation. Sample includes all bureaucrats, from high-level managers to service staff.}
    \label{fig:map_pooled}
\end{figure}
